Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
re-upload table III

@@

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.
See text for details}
\end{center}
\ref{fig:folds}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
early, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
late, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
late, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\caption{Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.}
\end{center}
\ref{table:dcase2013}
\end{table}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{folds.png}
\caption{Classification accuracies over the five folds of the DCASE 2013 private dataset, for various acoustic descriptors and temporal integration strategies. 
The chosen classifier is a support vector machine (SVM) whose kernel is a Gaussian radial basis function (RBF).
The mean accuracies and fold-wise standard deviations of each experiment are reported in Table \ref{table:dcase2013}.
See text for details}
\end{center}
\label{fig:folds}
\end{figure}

\begin{table}
\begin{center}
\begin{tabular}{llll}
             & MFCCs         & scattering & log-scattering  \\
             \hline
early, linear  & $54\pm20$   & $62\pm\phantom{0}6$  & $66\pm11$     \\
early, RBF     & $47\pm16$  & $56\pm\phantom{0}7$  & $63\pm\phantom{0}6$   \\
late, linear  & $60\pm\phantom{0}9$ & $70\pm\phantom{0}8$  & $75\pm\phantom{0}5$   \\
late, RBF     & $68\pm10$ & $73\pm\phantom{0}8$  & $\mathbf{78}\pm\phantom{0}6$   \\
\end{tabular}
\caption{Classification accuracies on the DCASE 2013 dataset with various settings of features, temporal integration strategies, and support vector machine kernels.}
\end{center}
\label{table:dcase2013}
\end{table}

@@

The results on the evaluation dataset are awaiting publication by the DCASE organizing committee.
Our results on the development dataset are reported in Table \ref{table:dcase2016}

\begin{table}
\begin{center}
\begin{tabular}{lcc}
Features & MFCCs & log-scattering \\
Classifier  & GMMs    & linear SVMs \\
Temporal integration & late (product rule) & late (majority voting) \\
\midrule
beach & $74.6 \pm 18.9$ & $83.5 \pm \phantom{0}7.1$ \\
bus & $58.2 \pm 18.3$ & $88.8 \pm 11.4$ \\
caf\'{e} / restaurant & $85.1 \pm 10.8$ & $64.5 \pm \phantom{0}8.3$ \\
car & $69.1 \pm 20.8$ & $94.9 \pm \phantom{0}6.1$ \\
city center & $89.6 \pm \phantom{0}9.2$ & $91.7 \pm \phantom{0}9.4$ \\
forest path & $72.4 \pm 23.8$ & $93.8 \pm \phantom{0}7.8$ \\
grocery store & $74.1 \pm 13.7$ & $90.9 \pm \phantom{0}6.9$ \\
home & $78.1 \pm 17.7$ & $56.2 \pm 23.9$ \\
library & $65.1 \pm 23.3$ & $82.0 \pm 13.0$ \\
metro station & $85.2 \pm 15.6$ & $96.0 \pm \phantom{0}2.3$ \\
office & $90.8 \pm 16.0$ & $87.5 \pm 21.7$ \\
park & $25.6 \pm 11.0$ & $75.4 \pm \phantom{0}7.4$ \\
residential area & $75.1 \pm 19.4$ & $44.2 \pm 15.0$ \\
train & $34.1 \pm \phantom{0}7.2$ & $58.3 \pm 10.0$ \\
tram & $85.4 \pm 13.9$ & $83.7 \pm 12.2$ \\
\bottomrule
Average & $70.8 \pm \phantom{0}2.6$ & $79.4 \pm \phantom{0}3.0$
\end{tabular}
\end{center}
\label{table:dcase2016}
\caption{Class-wise accuracies on the DCASE 2016 dataset for two pipelines: a baseline of mel-frequency cepstral coefficients (MFCCs), Gaussian mixture models (GMMs), and late temporal integration by product of likelihoods ; and our proposed algorithm of log-scattering coefficients, support vector machines (SVMs) with a linear kernel, and late temporal integration by majority voting. See text for details.}
\end{table}
